### 2017-08-25 reports/thesis/book.tex
Corrected simulation section in thesis.

The saddlepoint approximation was computed up to a constant using
\begin{equation}
p_X(x) \propto \exp\left[
-\frac{\alpha+2}{2(\alpha+1)}\ln(x)
-x\beta
+\left(
\frac{x\beta}{\alpha}
\right)^{\frac{\alpha}{\alpha+1}}\lambda^{\frac{1}{\alpha+1}}(\alpha+1) - k
\right]
\end{equation}
for 500 equally spaced points from and including the minimum non-zero simulated value to the maximum simulated value. $k$ is some constant to control over/underflow and it was chosen to be
\begin{equation}
k = \max_{i\in\text{simulation}}\left[
-\frac{\alpha+2}{2(\alpha+1)}\ln(x_i)
-x_i\beta
+\left(
\frac{x_i\beta}{\alpha}
\right)^{\frac{\alpha}{\alpha+1}}\lambda^{\frac{1}{\alpha+1}}(\alpha+1)
\right] \ .
\end{equation}
The density was then was normalised by numerically integrating it using the trapezium rule using the 500 evaluated points.

A Q-Q plot is a plot which compares the empirical with the theoretical c.d.f. Suppose realizations of $X$ were simulated $\left\{x_1,x_2,x_3,\dotdotdot,x_n\right\}$, let
\begin{equation}
F_X(x) = \prob(X\leqslant x)
\end{equation}
\begin{equation}
\widehat{F}_X(x) = \frac{1}{n}\cdot\text{max}\left[
\left(\sum_{i=1}^n\mathbb{I}(x_i\leqslant x)\right)-0.5,0
\right] \ ,
\end{equation}
then a Q-Q plot plot is a parametric plot which plots $\widehat{F}_X^{-1}(p)$ against $F_X^{-1}(p)$ for $p=\frac{0.5}{n},\frac{1.5}{n},\frac{2.5}{n},\dotdotdot,\frac{n-0.5}{n}$. If $F_X(x)$ and $\widehat{F}_X(x)$ are similar, a Q-Q plot should be a straight line with gradient 1, intercepting the origin. However there is no closed form for $F_X(x)$. When using the exact or saddlepoint method, $F_X(x)$ was found numerically by evaluating the p.d.f.~at $10\,000$ equally spaced points from and including the minimum to the maximum of the simulated samples, and then summing the required trapeziums. $\widehat{F}_X^{-1}(p)$ was then calculated by interpolation. For the saddlepoint approximation where $x=0$ cannot be evaluated, the lower limit of the numerical integral was chosen, arbitrary, to be
\begin{equation}
\frac{\euler^{-\lambda}\lambda\cdot\text{min}\left(\text{non-zero samples}\right)}{\euler^{-\lambda}(1+\lambda)}\times 0.1 \ .
\end{equation}

>>>>

Suppose realizations of $X$ were simulated $\left\{x_1,x_2,x_3,\dotdotdot,x_n\right\}$. The saddlepoint approximation was computed up to a constant using
\begin{equation}
p_X(x) \propto \exp\left[
-\frac{\alpha+2}{2(\alpha+1)}\ln(x)
-x\beta
+\left(
\frac{x\beta}{\alpha}
\right)^{\frac{\alpha}{\alpha+1}}\lambda^{\frac{1}{\alpha+1}}(\alpha+1) - k
\right]
\end{equation}
for 500 equally spaced points from and including the minimum non-zero simulated value to the maximum simulated value. $k$ is some constant to control over/underflow and it was chosen to be
\begin{equation}
k = \max_{i\in\left\{1,2,3,\dotdotdot,n\right\}}\left[
-\frac{\alpha+2}{2(\alpha+1)}\ln(x_i)
-x_i\beta
+\left(
\frac{x_i\beta}{\alpha}
\right)^{\frac{\alpha}{\alpha+1}}\lambda^{\frac{1}{\alpha+1}}(\alpha+1)
\right] \ .
\end{equation}
The density was then was normalised by numerically integrating it using the trapezium rule using the 500 evaluated points.

A Q-Q plot is a plot which compares the empirical with the theoretical c.d.f. Let
\begin{equation}
F_X(x) = \prob(X\leqslant x)
\end{equation}
\begin{equation}
\widehat{F}_X(x) = \frac{1}{n}\cdot\text{max}\left[
\left(\sum_{i=1}^n\mathbb{I}(x_i\leqslant x)\right)-0.5,0
\right] \ ,
\end{equation}
then a Q-Q plot plot is a parametric plot which plots $\widehat{F}_X^{-1}(p)$ against $F_X^{-1}(p)$ for $p=\frac{0.5}{n},\frac{1.5}{n},\frac{2.5}{n},\dotdotdot,\frac{n-0.5}{n}$. If $F_X(x)$ and $\widehat{F}_X(x)$ are similar, a Q-Q plot should be a straight line with gradient 1, intercepting the origin. However there is no closed form for $F_X(x)$. When using the exact or saddlepoint method, $F_X(x)$ was found numerically by evaluating the p.d.f.~at $10\,000$ equally spaced points from and including the minimum to the maximum of the simulated samples, and then summing the required trapeziums. $\widehat{F}_X^{-1}(p)$ was then calculated by interpolation. For the saddlepoint approximation where $x=0$ cannot be evaluated and their exist a zero value in the sample, the lower limit of the numerical integral was chosen, arbitrary, to be
\begin{equation}
\frac{\euler^{-\lambda}\lambda\cdot\text{min}\left(\text{non-zero samples}\right)}{\euler^{-\lambda}(1+\lambda)}\times 0.1 \ .
\end{equation}
